### 2013-11-15 tests_Housing.Rmd
add comparisation between reg & non reg GA.Poly

>>>>

########################################################
# Compare versions of GA.Poly (with vs without regularization)

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=30, iterations=25, lambda=0.8, runs=5)

save(report, file="Housing300_lambda0.8.vs.no.reg.Rda") # recover with load("Housing300.Rda")
